An Evaluation of RDF Constraint Types to Validate Metadata on Person-Level and Aggregated Data

### 2015-04-08 paper/paper7/paper7-evaluation.tex
evaluation

\section{Introduction}

\section{Disco}

\begin{itemize}
	\item DwB Resource Discovery Portal
	\begin{itemize}
	  \item Metadata records for each study are available on the study landing pages.
		\item \url{http://dwb-dev.nsd.uib.no/portal/#/study/http://portal.dwbproject.org/resource/Study/de.gesis/zacat/ZA5597/en}
    \item Search interface: \url{http://dwb-dev.nsd.uib.no/portal/#/search?q=smoking&p=1&s=score&d=desc&f=text}
	\end{itemize}
\end{itemize}

\section{Data Cube}

\begin{itemize}
	\item \url{http://270a.info/} (see the VoID which points to other
VoIDs) is full of data sets (probably close to 10k) using RDF Data Cube,
and some of those also include XKOS.
\end{itemize}

>>>>

\section{Evaluation}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccc@{}}
           & \multicolumn{6}{c}{\textbf{Vocabularies}}
    \\  \cmidrule{2-7}
    \\       \textbf{Criteria (Counts)}
           & \textbf{\rot{Person-Level Metadata (Disco)}}
           & \textbf{\rot{Aggregated Metadata (Data Cube)}}
					 & \textbf{\rot{Thesauri (SKOS)}}
					 & \textbf{\rot{Rectangular Data (PHDD)}}
					 & \textbf{\rot{Statistical Classifications (XKOS)}}
					 & \textbf{\rot{Total}}
    \\ \midrule
		\emph{Validated Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 \\
		\emph{Validated Data Sets} & 1,526 & 9,990 & 4,178 \\
		\hline
		\emph{Constraint Violations} & \textcolor{red}{XXXXX} \\
		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & \textcolor{red}{XXXXX} \\
		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & 473,574 $\equiv$ \textcolor{red}{XXXXX}\% \\
    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & \textcolor{red}{XXXXX} \\
				\hline
		\emph{Constraint Types} & 52 (15\textbar 37) \\
		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 30 $\equiv$ 57.7 \% \\
		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 22 $\equiv$ 42.3 \% \\
		\hline
		\emph{Constraints} & 142 (77\textbar 65) \\
		\emph{Constraints} ($\mathcal{C}_{C}$) & 72 $\equiv$ 50.7 \% \\
		\emph{Constraints} ($\mathcal{C}_{T}$) & 70 $\equiv$ 49.3 \% \\
		\emph{Constraints ($\mathcal{SL}_{0}$)} & 75 $\equiv$ 52.8\% (44\textbar 31)\\
		\emph{Constraints ($\mathcal{SL}_{1}$)} & 9 $\equiv$ 6.3\% (8\textbar 1)\\
		\emph{Constraints ($\mathcal{SL}_{2}$)} & 58 $\equiv$ 40.8\% (25\textbar 33)\\
    \bottomrule
    \end{tabular}
    \caption{Evaluation}
		\label{tab:evaluation}
    \end{center}
\end{table}

\subsection{Legend}

\begin{table}
	\centering
		\begin{tabular}{c|l}
      \textbf{Symbol} & \textbf{Description} \\		
			\textbf{\emph{X}} & Validation Successful \\
			\hline
			\textbf{\textgreater \emph{X}} & Poor Performance/Scaling \\
			\hline
      \ding{55} & Very Poor Performance/Scaling \\
			\hline
			\textbf{\emph{(!)}} & Not Yet Implemented Constraint \\
			\hline
			\textbf{\emph{(X)}} & The validation of \emph{X} data sets could not be finished \\
			           & due to SPARQL endpoints' technical restrictions (e.g. the defined timeout). \\
			\hline
			\textbf{\emph{\textsuperscript{*}}} & severity level $\mathcal{SL}_{0}$ (informational) \\
			\hline
			\textbf{\emph{\textsuperscript{**}}} & severity level $\mathcal{SL}_{1}$ (warning) \\
			\hline
			\textbf{\emph{\textsuperscript{***}}} & severity level $\mathcal{SL}_{2}$ (error) \\
		\end{tabular}
	\caption{Legend}
	\label{tab:legend}
\end{table}

\textbf{Validation Successful:} 
\emph{X} indicates the number of raised constraint violation triples.

\textbf{Poor Performance/Scaling:}
The performance of the implementation of the underlying SPARQL CONSTRUCT query 
is too poor to get all resulting constraint violation triples. 
Therefore, a limit of \emph{X} result constraint violation triples is set. 
It is likely that there are more than \emph{X} constraint violations.
Although, the result set contains not the whole set of raised constraint violation triples,
the constraint can be used as an indicator if there data not conforming to the constraint and
to resolve constraint violations step by step. 
As part of future work, the performance will be improved.

\textbf{Very Poor Performance/Scaling:} 
The performance of the implementation of the underlying SPARQL CONSTRUCT query 
is too poor to get any results, even though a limit of result constraint violation triples is set. 
As part of future work, the performance will be improved.

\section{Person-Level Metadata (Disco)}

\subsection{Evaluation Results}

Legend: total (implemented\textbar not yet implemented)

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Evaluation Criteria} & \textbf{Counts} \\		
      \hline
		\emph{Validated Triples} & 9,673,055 \\
		\emph{Validated Data Sets} & 1,526 \\
		\hline
		\emph{Constraint Violations} & \textcolor{red}{XXXXX} \\
		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & \textcolor{red}{XXXXX} \\
		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & 473,574 $\equiv$ \textcolor{red}{XXXXX}\% \\
    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & \textcolor{red}{XXXXX} \\
		\hline
		\emph{Constraint (Most Constraint Violations)} & \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} (547,916) \\
		                                               & \emph{DISCO-C-COMPARISON-VARIABLES-02} (547,916) \\
		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{0}$))} & \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} (547,916) \\
		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{1}$))} & \emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-46} (468,807) \\
		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{2}$))} & \emph{DISCO-C-COMPARISON-VARIABLES-02} (547,916) \\
		\hline
		\emph{Constraint Types} & 52 (15\textbar 37) \\
		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 30 $\equiv$ 57.7 \% \\
		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 22 $\equiv$ 42.3 \% \\
		\hline
		\emph{Constraint Types (Most Constraints)} & 1. Existential Quantifications: 46 $\equiv$ 32.4\% (46\textbar 0) \\
		                                            & 2. Data Model Consistency: 7 (1\textbar 6) \\
																								& 3. Aggregation: 7 (0\textbar 7) \\
		\emph{Constraint Type (Most Constraints ($\mathcal{SL}_{2}$))} & Existential Quantifications: 9 (9\textbar 0) \\
		\hline
		\emph{Constraints} & 142 (77\textbar 65) \\
		\emph{Constraints} ($\mathcal{C}_{C}$) & 72 $\equiv$ 50.7 \% \\
		\emph{Constraints} ($\mathcal{C}_{T}$) & 70 $\equiv$ 49.3 \% \\
		\emph{Constraints ($\mathcal{SL}_{0}$)} & 75 $\equiv$ 52.8\% (44\textbar 31)\\
		\emph{Constraints ($\mathcal{SL}_{1}$)} & 9 $\equiv$ 6.3\% (8\textbar 1)\\
		\emph{Constraints ($\mathcal{SL}_{2}$)} & 58 $\equiv$ 40.8\% (25\textbar 33)\\
		\end{tabular}
    \caption{Evaluation of Disco Data Sets - Evaluation Results}
		\label{tab:disco-evaluation-results}
\end{table}

%\begin{table}[H]
    %\begin{center}
    %\begin{tabular}{@{}lc@{}}
           %& \multicolumn{1}{c}{\textbf{Constraint Types}}
    %\\  \cmidrule{2-2}
    %\\       \textbf{Criteria (Counts)}
           %& \textbf{\rot{Existential Quantifications}}
    %\\ \midrule
		%\emph{Constraints / Constraint Type} & 46 \\
    %\bottomrule
    %\end{tabular}
    %\caption{Evaluation of Disco Data Sets - Evaluation Results (2)}
		%\label{tab:disco-evaluation-results-2}
    %\end{center}
%\end{table}

\subsection{Data Sets Overview}

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Abbr.} & \textbf{Disco Data Sets} \\		
      \hline
    \emph{Missy} & \emph{Microdata Information System}\tablefootnote{\url{http://www.gesis.org/missy/eu/missy-home}} \\
		\emph{DwB} & \emph{DwB Discovery Portal}\tablefootnote{\url{http://dwb-dev.nsd.uib.no/portal}} \\
		\emph{DDA-SND} & \emph{DDI-RDF}\tablefootnote{\url{http://ddi-rdf.borsna.se/}} \\
		               & provided by the \emph{Danish Data Archive (DDA)}\tablefootnote{\url{http://samfund.dda.dk/dda/default-en.asp}} and Swedish National Data Service (SND)\tablefootnote{\url{http://snd.gu.se/en}} \\ 
		\end{tabular}
	\caption{Disco Data Sets Abbreviations}
	\label{tab:disco-data-sets-abbreviations}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccccccccccc@{}}
           & \multicolumn{9}{c}{\textbf{Counts}}
    \\  \cmidrule{2-10}
    \\       \textbf{Data Sets}
           & \textbf{\rot{triples}}
           & \textbf{\rot{disco:StudyGroup}}
           & \textbf{\rot{disco:Study}}
           & \textbf{\rot{disco:LogicalDataSet}}
           & \textbf{\rot{disco:Universe}}
					 & \textbf{\rot{disco:Variable}}
					 & \textbf{\rot{disco:Question}}
				   & \textbf{\rot{disco:SummaryStatistics}}
					 & \textbf{\rot{disco:CategoryStatistics}}
					 & \textbf{\rot{skos:Concept}}
    \\ \midrule
    \emph{Missy} & 5,068,838 & 6 & 45 & 159 & 1,125 & 21,040 & 0 & 0 & 0 & 147,193 \\
		\emph{DwB} & 2,332,802 & 0 & 1,387 & 1,367 & 2,796 & 446,806 & 0 & 0 & 0 & 0 \\
		\emph{DDA-SND} & 2,271,415 & 0 & 1,490 & 0 & 10,188 & 80,070 & 139,237 & 0 & 0 & 290,963 \\ 
		\hline
		\textbf{\emph{Total}} & 9,673,055 & & & 1,526 \\
    \bottomrule
    \end{tabular}
    \caption{Disco Data Sets Overview}
		\label{tab:disco-overview}
    \end{center}
\end{table}

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Data Sets} & \textbf{SPARQL Endpoint} \\		
      \hline
      \emph{Missy} & \url{http://svko-missy:8181/openrdf-workbench/repositories/native-java-store/summary} \\
			\emph{DwB} & \url{http://dwb-dev.nsd.uib.no/sparql} \\
			\emph{DDA-SND} & \url{http://ddi-rdf.borsna.se/endpoint/} \\
		\end{tabular}
	\caption{Disco SPARQL Endpoints}
	\label{tab:disco-sparql-endpoints}
\end{table}

\subsection{Detailed Evaluation}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Existential Quantifications (1)}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-02}\textsuperscript{***} & 7 & 17 & 1,490 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-03}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-04}\textsuperscript{*} & 11,021 & 445,381 & 62,260 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-05}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & 139,237 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-06}\textsuperscript{*} & 12 & 1,367 & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-07}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-08}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-09}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-10}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Existential Quantifications (1)}
		\label{tab:evaluation-disco-existential-quantifications-1}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Existential Quantifications (2)}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-11}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-12}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-13}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-14}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-15}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-16}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-17}\textsuperscript{*} & 159 & 1,367 & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-18}\textsuperscript{*} & 159 & 1,367 & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-19}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-20}\textsuperscript{*} & $\checkmark$ & 1,367 & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Existential Quantifications (2)}
		\label{tab:evaluation-disco-existential-quantifications-2}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Existential Quantifications (3)}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-21}\textsuperscript{*} & $\checkmark$ & 1,367 & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-22}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-23}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-24}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-25}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-26}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-27}\textsuperscript{***} & $\checkmark$ & 130 & 1,490 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-28}\textsuperscript{**} & 159 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-29}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-30}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Existential Quantifications (3)}
		\label{tab:evaluation-disco-existential-quantifications-3}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Existential Quantifications (4)}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-31}\textsuperscript{**} & 159 & 1,367 & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-32}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-33}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-34}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-35}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-36}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-37}\textsuperscript{*} & 18,625 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-38}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & 750 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-39}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-40}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & 139,237 \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Existential Quantifications (4)}
		\label{tab:evaluation-disco-existential-quantifications-4}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Existential Quantifications (5)}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-41}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-42}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-43}\textsuperscript{*} & 15,733 & 446,806 & 80,070 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-44}\textsuperscript{*} & 159 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-45}\textsuperscript{*} & 6,784 & 446,806 & 19,221 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-46}\textsuperscript{**} & 11,550 & 446,806 & 10,451 \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Existential Quantifications (5)}
		\label{tab:evaluation-disco-existential-quantifications-5}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Conditional Properties}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{ DISCO-C-CONDITIONAL-PROPERTIES-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & 80,070 \\
		\emph{ DISCO-C-CONDITIONAL-PROPERTIES-02}\textsuperscript{**} & 12 & $\checkmark$ & $\checkmark$ \\
		\emph{ DISCO-C-CONDITIONAL-PROPERTIES-03}\textsuperscript{**} & 90 & $\checkmark$ & 2,980 \\
		\emph{ DISCO-C-CONDITIONAL-PROPERTIES-04}\textsuperscript{***} & 6 & $\checkmark$ & $\checkmark$ \\
		\emph{ DISCO-C-CONDITIONAL-PROPERTIES-05}\textsuperscript{***} & 45 & 1,387 & 1,490 \\
		\emph{ DISCO-C-CONDITIONAL-PROPERTIES-06}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Conditional Properties}
		\label{tab:evaluation-disco-conditional-properties}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Provenance}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-PROVENANCE-01}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-PROVENANCE-02}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
		\emph{DISCO-C-PROVENANCE-03}\textsuperscript{*} & 159 & 1,367 & $\checkmark$ \\
		\emph{DISCO-C-PROVENANCE-04}\textsuperscript{*} & $\checkmark$ & 1,367 & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Provenance}
		\label{tab:evaluation-disco-provenance}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Labeling and Documentation}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-LABELING-AND-DOCUMENTATION-01}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-LABELING-AND-DOCUMENTATION-02}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
		\emph{DISCO-C-LABELING-AND-DOCUMENTATION-03}\textsuperscript{*} & 159 & 1,367 & $\checkmark$ \\
		\emph{DISCO-C-LABELING-AND-DOCUMENTATION-04}\textsuperscript{*} & $\checkmark$ & 1,367 & $\checkmark$ \\
		\emph{DISCO-C-LABELING-AND-DOCUMENTATION-05}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-LABELING-AND-DOCUMENTATION-06}\textsuperscript{*} & 21,040 & 446,806 & 80,070 \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Labeling and Documentation}
		\label{tab:evaluation-disco-labeling-and-documentation}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Data Model Consistency}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-DATA-MODEL-CONSISTENCY-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-02 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-03 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-04 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-05}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-06 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-07 (!)}\textsuperscript{***} \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Data Model Consistency}
		\label{tab:evaluation-disco-data-model-consistency}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Comparison}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-COMPARISON-VARIABLES-01 (!)}\textsuperscript{**} \\
		\emph{DISCO-C-COMPARISON-VARIABLES-02}\textsuperscript{***} & 21,040 & 446,806 & 80,070 \\
		\emph{DISCO-C-COMPARISON-VARIABLES-03 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-COMPARISON-VARIABLES-04}\textsuperscript{*} & 18,625 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-COMPARISON-VARIABLES-05}\textsuperscript{***} & 159 & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Comparison}
		\label{tab:evaluation-disco-comparison}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Mathematical Operations}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-MATHEMATICAL-OPERATIONS-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-MATHEMATICAL-OPERATIONS-02 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-MATHEMATICAL-OPERATIONS-03 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-MATHEMATICAL-OPERATIONS-04 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-MATHEMATICAL-OPERATIONS-05 (!)}\textsuperscript{***} \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Mathematical Operations}
		\label{tab:evaluation-disco-mathematical-operations}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Language Tags}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-LANGUAGE-TAG-MATCHING-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-LANGUAGE-TAG-CARDINALITY-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-LANGUAGE-TAG-CARDINALITY-02 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-LANGUAGE-TAG-CARDINALITY-03 (!)}\textsuperscript{*} \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Language Tags}
		\label{tab:evaluation-disco-language-tags}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Aggregation}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-AGGREGATION-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-AGGREGATION-02 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-AGGREGATION-03 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-AGGREGATION-04 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-AGGREGATION-05 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-AGGREGATION-06 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-AGGREGATION-07 (!)}\textsuperscript{*} \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Aggregation}
		\label{tab:evaluation-disco-aggregation}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Disco Constraints}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-ALLOWED-VALUES-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-LITERAL-RANGES-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-INVERSE-FUNCTIONAL-PROPERTIES-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-INVERSE-FUNCTIONAL-PROPERTIES-02}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-CLASS-SPECIFIC-PROPERTY-RANGE-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-MEMBERSHIP-IN-CONTROLLED-VOCABULARIES-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & \ding{55} \\
		\emph{DISCO-C-LITERAL-VALUE-COMPARISON-01}\textsuperscript{***} & $\checkmark$ & 1,299 & $\checkmark$ \\
		\emph{DISCO-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01}\textsuperscript{*} & 21,038 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-DATA-PROPERTY-FACETS-01}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-DATA-PROPERTY-FACETS-02}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Disco Constraints (1)}
		\label{tab:evaluation-disco-disco-constraints-1}
    \end{center}
\end{table}
